---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fdistr

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/dtminnick/fdistr.svg?branch=master)](https://travis-ci.org/dtminnick/fdistr)
[![CRAN status](https://www.r-pkg.org/badges/version/fdistr)](https://CRAN.R-project.org/package=fdistr)
[![Codecov test coverage](https://codecov.io/gh/dtminnick/fdistr/branch/master/graph/badge.svg)](https://codecov.io/gh/dtminnick/fdistr?branch=master)
<!-- badges: end -->

The fdistr package provides an efficient way to create frequency distribution
tables and use those tables to generate Pareto charts.  

Frequency distribution tables show the frequency of various outcomes
in a data set.  Each entry in the table contains a frequency or count of 
values within a particular group or interval, and in this way, the table 
summarizes the distribution of values in the data set.  

A Pareto chart visually depicts the frequency distribution table.

## Installation

You can install the released version of fdistr from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("fdistr")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("dtminnick/fdistr")
```
## Example

This basic example which shows you how to use the fdistr package with the 
built-in `words` dataset.

Start by loading the `words` dataset.  The dataset contains a data frame with 
six variables about a collection of words taken from the first paragraph of 
James Joyce's short story "The Dead."  

```{r}
library(fdistr)

data(words)

str(words)
```

It is possible to create a frequency distribution table with any of the six
variables in this table.  For this example, pass the `first_letter` variable 
to the `create_table` function and return the table (stored as a data frame) 
to a variable called `table`.  Use the `dec_pos` argument to set the number 
of positions following the decimal to be displayed in the table.

```{r}
table <- create_table(words$first_letter, dec_pos = 3)

table
```

In this example, the frequency distribution table provides a row for each unique 
first letter in the dataset, arranged in descending order of count, with the 
frequency, cumulative count and cumulative frequency for each first letter.

To plot the data in a Pareto chart, pass the `table` data frame to the 
`create_pareto` function along with character strings for the plot labels.

```{r}
create_pareto(table,
              title = "Pareto Chart",
              subtitle = "Frequency of first letters in Joyce's 'The Dead'",
              x_label = "Letter",
              y_label = "Frequency",
              caption = "Chart generated using the built-in words data.")
```

Bars in the chart show the frequency of each first letter and a line shows the
cumulative frequency with points to highlight the cumulative frequency for each
value above the bars.  The Pareto chart is an effective way to show the frequencies
of values.