---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fdistr

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/dtminnick/fdistr.svg?branch=master)](https://travis-ci.org/dtminnick/fdistr)
<!-- badges: end -->

The goal of fdistr is to provide an efficient way to create frequency distribution
tables and use those tables to generate Pareto charts.  

A frequency distribution is a table that shows the frequency of various outcomes
in a data set.  Each entry in the table contains a frequency or count of the 
occurrences of values within a particular group or interval, and in this way, 
the table summarizes the distribution of values in the data set.  

A Pareto chart is a bar graph visually depicts the frequency distribution table.

## Installation

You can install the released version of fdistr from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("fdistr")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("dtminnick/fdistr")
```
## Example

This is a basic example which shows you how to use the fdistr package.

```{r example}
# library(fdistr)
# data(words)
# table <- create_table(words$first_letter)
# table
# create_pareto(table)
```
