---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fdistr

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/dtminnick/fdistr.svg?branch=master)](https://travis-ci.org/dtminnick/fdistr)
[![CRAN status](https://www.r-pkg.org/badges/version/fdistr)](https://CRAN.R-project.org/package=fdistr)
<!-- badges: end -->

The goal of fdistr is to provide an efficient way to create frequency distribution
tables and use those tables to generate Pareto charts.  

Frequency distribution tables are used to show the frequency of various outcomes
in a data set.  Each entry in the table contains a frequency or count of the 
occurrences of values within a particular group or interval, and in this way, 
the table summarizes the distribution of values in the data set.  

A Pareto chart is a bar graph visually depicts the frequency distribution table.

## Installation

You can install the released version of fdistr from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("fdistr")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("dtminnick/fdistr")
```
## Example

What follows is a basic example which shows you how to use the fdistr package with the built-in `words` dataset.

Start by loading the `words` dataset.  The dataset contains a data frame with four variables about a collection of words taken from the first paragraph of James Joyce's short story "The Dead."  

```{r}
library(fdistr)

data(words)

str(words)
```

It is possible to create a frequency distribution table with any of the four
variables in this table.  For this example, pass the `first_letter` variable to the `create_table` function and return the table (stored as a data frame) to a variable
called `table`.  Use the `dec_pos` argument to set the number of positions 
following the decimal to be displayed in the table.

```{r}
table <- create_table(words$first_letter,
                      dec_pos = 3)

table
```

In this case, the frequency distribution table provides a row for each unique 
first letter in the dataset, arranged in descending order of count, with the frequency, cumulative count and cumulative frequency for each first letter.

To plot the data in a Pareto chart, pass the `table` data frame to the 
`create_pareto` function along with character strings for the plot labels.

```{r}
create_pareto(table,
              title = "Pareto Chart",
              subtitle = "Frequency of first letters in Joyce's 'The Dead'",
              x_label = "Letter",
              y_label = "Frequency",
              caption = "Chart generated using the built-in words data.")
```
